---
title: "R Solution"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(huxtable)
```
Plan of the work:  

- Delete columns having unique ID, too many NAs not interpretable/meaningful ones  

- Lump all >5 and <30 labels as 'Yes', also delete the rows with label==NA 

- Feature selection/importance and reduction  

- May use RF, ANN and Naive Bayes  

## Original Dataset  

A glimpse into 100 random rows of the dataset is given below:  

```{r}
dt_original  <- read.csv("Blood_Pressure_data.csv", stringsAsFactors=TRUE)
DT::datatable(dt_original[sample(nrow(dt_original),100),])
```
  
### Structure of Original Data  
  
Structure of the dataset is given below:

```{r}
glimpse(dt_original)
dt_original[dt_original=="?"] <- NA
```

## Health of Variables  

Dataset health may be seen by following table:

```{r}
skm_original <- skimr::skim(dt_original)
skm_original %>% filter(complete_rate<0.999999) %>% 
  select(skim_variable, n_missing, complete_rate, factor.n_unique) %>% 
  rename(Variable=skim_variable,Missings=n_missing,CompletenessRate=complete_rate,Uniques=factor.n_unique) %>% 
  arrange(CompletenessRate) %>% 
  as_huxtable(add_colnames=T) %>% set_top_border(row=2, value = 0.4)
```

## Cleaning Tasks  
On the basis of above data health table and other Machine Learning considerations we drop certain columns and also apply a transformation on label variable. Details of these cleaning steps are as follows:  

- Replace all "?" with NA (Not Available).  

- Variables: *id, weight, discharge_disposition_id, admission_source_id, patient_no and admission_typeid* are useless because of having more than 10 factors   
- Variables *payer_code and medical_specialty* have very high number of factors 17 and 72, respectively.  Moreover they contain integer and alphanumeric factors simultaneously.  

- *examide and citoglipton* have only 1 factor throughout i.e. have 0 variance  

- Factors '>5' and '<30' have been lumped together in new category named 'YES'.

- Variable age.group has been designated as an ordinal categorical variable.  

## Cleaned Dataset  

```{r}
dt <- dt_original %>% 
  select(-c(id, weight, discharge_disposition_id, admission_source_id, patient_no, admission_typeid)) %>%   # useless cols e.g. Id's and having more than 10 factors
  select(-c(payer_code, medical_specialty)) %>%   # high cardinality factor variables respectively 17 and 72
  select(-c(diag_1, diag_2, diag_3)) %>%   # useless because these contain integer and V## type mixed entries, factors are more than 700
  select(-c(examide,citoglipton)) %>%      # have only 1 factor throughout 
  mutate(label=fct_recode(dt_original$label,YES=">5",YES="<30"),
         age.group=factor(age.group,ordered=T)
         )
```


```{r}
skm <- skimr::skim(dt)
skm
```
### Structure of Cleaned Data  

Structure of the cleaned dataset is given below:
```{r}
glimpse(dt)
```

## Class Balance  

It is an almost balanced dataset in terms of classes:
```{r}
table(dt$label) %>% as.data.frame() %>% rename(Label=Var1) %>%  as_huxtable(add_colnames=T) %>% set_top_border(row=2, value = 0.4)
```
  
Difference of 7962 between YES and NO is negligible because the total available labels are 101766.  

